Preliminary Thesis Defence

### 2014-01-02 south-africa.tex
data description

For adults several variables measure the different amounts and sources of income.
Among those, a variable if the adult receives a state pension, and if so, how much.
This is a numeric variable, the values of which lie very close together.

@@

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores are calculated.
The following z-scores are included:

>>>>

\begin{table}[hb!]
\centering
\caption{Z-score distributions}
\label{sa:ta:zscore}
    \begin{tabular}{l|rrrr}
    \hline
    & HAZ & WAZ & WHZ & BMIZ\\
    \hline
    Min.   & -5.972 & -6.000  & -4.916 & -4.994 \\
    1st    & -1.768 & -1.110  & -0.302 & -0.602 \\
    Median & -0.941 & -0.310  &  0.491  & 0.207  \\
    Mean   & -0.956 & -0.296  &  0.501  & 0.240   \\
    3rd    & -0.132 &  0.516  &  1.351  & 1.069  \\
    Max.   &  5.975 &  4.958  &  4.967  & 4.992  \\
    \end{tabular}
\end{table}

For adults several variables measure the different amounts and sources of income.
Among those, a variable if the adult receives a state pension, and if so, how much.
This is a numeric variable, the values of which lie very close together.
We observe that 22.99\% of household in our dataset have a female pension recipient as part of the household.
Furthermore, we observe that 9.06\% of households in our dataset have a male pension recipient.
This implies that, despite the fact that men are now eligible at the same age as women,
the vast majority of pension recipients is female.
Therefore, there is still a selection bias issue in the data we are analysing.

@@

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores are calculated.
